\Title

### 2023-02-07 Grimaldi-etal-BiolCybernetics.tex
intro : a

\noindent %The paper is available a an~\href{https://arxiv.org/abs/2205.03635}{arXiv preprint} with links to previous versions ands to the code. 
Find also the associated~\href{https://www.zotero.org/groups/4776796/fastmotiondetection}{zotero group} used to regroup relevant literature on the subject.

@@

The human brain has the remarkable property of being able to react at any time, while consuming a reasonable amount of energy, about tens of watts. This system is the result of millions of years of natural selection, and a striking difference between biological neural networks and artificial ones is the representation they use. Convolutional Neural Networks (CNNs), for example, represent information passing from one layer to another as tensors storing visual information densely over the visual topography, while representing different properties in different channels. These networks have been known to mimic many properties of biological systems~\citep{schrimpf_brain-score_2020}, yet, this score does not account for rapidity or energy consumption. On the other hand, information in a large majority of biological neural networks is represented as \emph{spikes}, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted this spike~\citep{paugam-moisy_computing_2012}. While CNNs obtain state-of-the-art performances for some computer vision tasks like image recognition, they do not make use of the dynamics inherent to the way we sense our natural environment. The third generation of artificial neural networks, i.e. Spiking Neural Networks (SNNs), include this temporal dimension in their computations. This new kind of algorithms are interesting for computational neuroscience as they represent a better model of biological neurons. Some approaches have designed normative models of SNNs that aim to have applications in machine learning. One of these is the SpikeNet algorithm, which uses a purely temporal approach by encoding information using one spike per neuron~\citep{delorme_spikenet_1999}. Another type of SNN using precise spike timing attempts to determine the structure of the network in order to minimize a cost function. This was implemented in the SpikeProp algorithm~\citep{bohte_error-backpropagation_2002} and has been extended in novel gradient-based methods. The surrogate gradient method is now widely used in methods that attempt to transfer performance from CNNs to SNNs~\citep{zenke_remarkable_2021}. However, the performance of SNNs is still lagging that of firing rate-based networks and the question of the advantage of using spikes in machine learning and computer vision remains open.

>>>>

\noindent %The paper is available a an~\href{https://arxiv.org/abs/2205.03635}{arXiv preprint} with links to previous versions ands to the code. 
Find also the associated~\href{https://www.zotero.org/groups/4776796/fastmotiondetection}{zotero group} used to gather relevant literature on the subject.

@@

The human brain has the remarkable property of being able to react at any time while consuming a reasonable amount of energy, about tens of watts. This system is the result of millions of years of natural selection, and a striking difference between biological and artificial neural networks is the representation they use. Convolutional neural networks (CNNs), for example, represent the flow of information from one layer to another as tensors, storing visual information densely across the visual topography, with different properties represented in different channels. These networks are known to mimic many properties of biological systems, such that each can be attributed a ``Barin Score''~\citep{schrimpf_brain-score_2020}, yet this score takes no account of speed or energy consumption. CNNs have achieved state-of-the-art performance for some computer vision tasks, such as image recognition. However, they do not take advantage of the dynamics inherent in the way we perceive our natural environment. On the other hand, in the vast majority of biological neural networks, information is represented as \emph{spikes}, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted the spike~\citep{paugam-moisy_computing_2012}. The third generation of artificial neural networks, called Spiking Neural Networks (SNNs), incorporate this temporal dimension into how they compute. By providing a better model of biological neurons, these new algorithms are of interest to computational neuroscience. Some approaches have developed normative models of SNNs that aim to have applications in machine learning. One of these is the SpikeNet algorithm, which uses a purely temporal approach by encoding information using one spike per neuron~\citep{delorme_spikenet_1999}. Another type of SNN that uses accurate timing of spikes attempts to determine the structure of the network to minimize a cost function. This was implemented in the SpikeProp algorithm~\citep{bohte_error-backpropagation_2002} and has been recently extended in gradient-based methods. This surrogate gradient method is now widely used in methods that attempt to transfer the performance of CNNs to SNNs~\citep{zenke_remarkable_2021}. However, the performance of SNNs still lags behind that of firing rate based networks. The question of the advantage of using spikes in machine learning and computer vision remains open.
